\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-03 casestudies.tex

The first case study is the mechanization of the type safety theorem of
STLC and those of its extensions,
which has been occurring in the examples in this paper.
The code base is ported from Software Foundations~\cite{sf-pl}.
%
The base STLC family consists of about 400 lines of code.
Lines of code in each of the four derived families
($\mathrm{Y}$, $\times$, $+$, and $\mu$ in the Venn diagram)
vary from 100 to 300, largely depending on how many constructors they
add to the inductive types.

@@

>>>>

The first case study is the mechanization of the type safety theorem of
STLC and those of its extensions,
which has been occurring in the examples in this paper.
The code base is ported from Software Foundations~\cite{sf-pl}.
%
The base STLC family consists of about 400 lines of code.
Lines of code in each of the four derived families
($\mathrm{Y}$, $\times$, $+$, and $\mu$ in the Venn diagram)
vary from 100 to 250, largely depending on how many constructors they
add to the inductive types.

@@

\begin{itemize}
\item 
proofs similar to those in SF
\item
differences from SF:
    \begin{itemize}
    \item 
    axiomatized equalities on subst
    \item
    inversion lemmas
    \item
    \end{itemize}
\end{itemize}
